\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Siemens Healthineers}{Bangalore, India}
    {Software Engineer 1}{July 2023 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Engineered mission-critical medical imaging systems} operating in highly regulated environments, architecting distributed solutions for complex DICOM workflows using MVVM and microservices. Enhanced 7 of 11 imaging pipelines, ensuring reliability, scalability, and clinician-ready performance.}
      \resumeItem{\textbf{Architected CI/CD pipelines on AWS and Azure DevOps}, reducing deployment cycles by 40\% and enabling faster delivery of regulatory-compliant releases. Spearheaded migration from TFS to Git across product lines.}
      \resumeItem{\textbf{Identified edge cases} in imaging data and reducing production defects by \textbf{20\%} through \textbf{validation pipelines and automated test coverage}. Collaborated cross-functionally under \textbf{SAFe Agile}.}
      \resumeItem{Designed and implemented automated test suites using \textbf{NUnit/xUnit} and integration pipelines, increasing test coverage and supporting reliable, compliant releases.}
      \resumeItem{\textbf{Refactored legacy codebases into modular, test-driven components}, introducing design patterns and UML documentation aligned with IEC 62304 standards.}
      \resumeItem{\textbf{Developed RESTful APIs and WCF services} for seamless integration with PACS/HIS systems, optimizing serialization and secure communication protocols.}
      \resumeItem{\textbf{Drove adoption of SonarQube} for static analysis and improving \textbf{code quality} metrics by \textbf{25\%}. Mentored junior engineers and interns.}
      \resumeItem{Analyzed system \textbf{performance bottlenecks} across compute, memory, and I/O, applying profiling and optimization strategies to ensure \textbf{high throughput and reliability}.}
    \resumeItemListEnd

  \resumeSubheading
    {Siemens Healthineers}{Bangalore, India}
    {Software Engineer Intern}{February 2023 -- July 2023}
    \resumeItemListStart
      \resumeItem{Contributed to the design and implementation of a \textbf{scalable infrastructure} for a \textbf{medical imaging} software product, adhering to industry standards. Acquired experience in \textbf{Agile} methodologies and development best practices.}
      \resumeItem{Engineered a DevOps functionality using Angular for the front-end, .NET C\# for the back-end and interface, and \textbf{REST APIs} for communication with the server using \textbf{MVC} pattern, leading to \textbf{60\%} time saved in the process.}
    \resumeItemListEnd

  \resumeSubheading
    {Beneath-a-Tree}{India}
    {Techno-Managerial STEM Internship}{February 2022 -- March 2022}
    \resumeItemListStart
      \resumeItem{As a team of 4 STEM Trainers in Rural Gujarat for the STEM for Girls initiative, sparking interest in science and research. Planned events, communicated interculturally, and managed resources, logistics and execution.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
