\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Order-Matching-Engine} (\href{https://github.com/CodeWreckPro/Order-Matching-Engine}{Github}) $|$ \emph{C\#/C++, Docker, AWS}}{}
    \resumeItemListStart
      \resumeItem{Implemented high‑performance trading services in C\# with efficient \textbf{algorithms \& data structures} for order books; designed \textbf{multithreaded} execution with concurrency controls.}
      \resumeItem{Built \textbf{RESTful APIs} and ingestion workflows; containerized with Docker on AWS; added \textbf{retry/backoff} for resilient I/O and profiled to optimize throughput/latency.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{EchoLens – Code Analysis Tool} (\href{https://codewreckpro.github.io/Echelons_Code_Analysis_Tool/}{Live} $|$ \href{https://github.com/CodeWreckPro/Echelons_Code_Analysis_Tool}{Github}) $|$ \emph{AI, ML, 3D Visualization}}{}
    \resumeItemListStart
      \resumeItem{Created an AI‑powered platform that predicts risks, detects technical debt, and visualizes dependencies; implemented ML‑based hotspot prediction and semantic commit analysis.}
      \resumeItem{Developed pipelines for repository analysis; contributed to \textbf{architecture/design reviews}; delivered dashboards to guide refactoring and evaluation workflows.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Med-Pilot} (\href{https://github.com/CodeWreckPro/Med-Pilot}{Github}) $|$ \emph{FastAPI, PostgreSQL, OpenAI}}{}
    \resumeItemListStart
      \resumeItem{Developed an AI‑driven healthcare platform with \textbf{RESTful APIs} and \textbf{PostgreSQL} data modeling; deployed on Linux; implemented semantic search with embeddings.}
      \resumeItem{Built multi‑agent modules; \textbf{optimized queries \& indexing}; followed \textbf{Agile/SDLC}; delivered scalable APIs and dashboards for evaluation workflows.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Sales CRM – In‑House Web App} (\emph{Laravel, MySQL, HTML/CSS/JS})}{}
    \resumeItemListStart
      \resumeItem{Built a \textbf{Laravel} CRM supporting Corporate Sales workflows (leads, accounts, opportunities) with \textbf{Eloquent models}, migrations, and role‑based access.}
      \resumeItem{Implemented \textbf{RESTful APIs} and third‑party integrations (webhooks/OAuth); wrote \textbf{PHPUnit/integration tests} and user guides; deployed on Linux with Docker.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Secure File Encryption Utility} (\href{https://github.com/CodeWreckPro/AES_Encryption_and_Decryption_Script}{Github}) $|$ \emph{Python, AES}}{}
    \resumeItemListStart
      \resumeItem{Implemented \textbf{AES/CBC} encryption with PKCS\#7 padding; designed modular key management and robust error handling for reliability.}
      \resumeItem{Built CLI for usability; optimized byte‑level performance; adhered to \textbf{coding standards} and maintainable design.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Music Genre Classification} (\href{https://github.com/CodeWreckPro/Music_Genre_Classification}{Github}) $|$ \emph{Python, Librosa, scikit-learn}}{}
    \resumeItemListStart
      \resumeItem{Built ML pipeline for audio classification; implemented feature extraction and model training; achieved 67\% accuracy with cross‑validation.}
      \resumeItem{Created evaluation visualizations; documented \textbf{design decisions} and experiment results to guide improvements.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
